---
title: "Captive Index User Guide"
author: "Jack Lewton, Danny Norrey, Christian Devenish"
date: "19 August 2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Captive Index User Guide}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## 1.	Data Organization  
Data should be set out in the same format as in the `giraffe` example data file. Note that a warning will be given for any of the possible pairs not recorded together.

```{r}
library(CaptiveIndex)
data(giraffe)
head(giraffe)
```

Columns should include the following:
*  Subject - Individual being sampled 
*  Present – list of individuals present separate by a space 
*  N.N – names of individual who is the nearest neighbour (within x metres) 
*  C.P – names of individual who is within the closet proximity (within x metres) 

NB. If there is no individual for N.N or C.P record as a 0 (zero).

## 2.	Create a dataset for the association measures

Use `DataCreate` function to prepare data for analysis:

This function will identify the number of times pairs are together, providing a short hand descriptor of the pair using the first 3 letters of each individual. 

```{r} 
NN.ID <- DataCreate (giraffe)

head(NN.ID)

```

## 3. Calculate weights

Calculate the weights for nearest neighbour and proximity values using the `Weights` function:

```{r}

W <- Weights(giraffe)
W

```

## 4. Calculate Captive Index
Calculate the Captive Index (or association meassure) using the data created in the `DataCreate` function and applying the weights from `Weights` function:


```{r}
Results <- CaptiveIndex(NN.ID, W$NN, W$IDist)
head(Results)
```

## 5. Plot network using igraph (optional) 
Convert 'Results' output into a square matrix, then plot a sociogram using igraph.

```{r}
# reshape the data frame into a square matrix 
# install.packages("reshape2")
library(reshape2)
mat <- acast(Results, Subject ~ Partner, value.var = "CaptiveIndex1")
```

```{r, message = F}
# install.packages("igraph")
library(igraph)
## Plot graph with weighted edges
```

```{r, fig.width = 6, fig.height = 6}
g <- graph.adjacency(mat, mode="undirected", weighted=TRUE, diag=FALSE)

plot.igraph(g, vertex.label = V(g)$name,
            layout = layout.fruchterman.reingold, 
            edge.color = "black",
            edge.width = (E(g)$weight)*20, 
            mode = "circle")
```

